### 2023-03-02 manuscript.Rmd
Shorten long code lines
Make sure all keywords are in word2vec

  # Compute cosine similarities between rating study responses and keywords
  rating <-
    map2_dfc(rating_substantives, rating_verbs, str_c, sep = ", ") %>%
    mutate(participant_id = rating_raw$CASE) %>%
    pivot_longer(
      -participant_id,
      names_to = "question_id", values_to = "response"
    ) %>%
    bind_cols(keywords_for_rating, .) %>%
    pivot_longer(
      c(match, nonmatch),
      names_to = "condition", values_to = "keywords"
    ) %>%
    mutate(across(c(keywords, response), str_to_lower)) %>%
    mutate(cosine = compute_cosine(keywords, response, word2vec))

@@

>>>>

  # Compute cosine similarities between rating study responses and keywords
  rating <-
    map2_dfc(rating_substantives, rating_verbs, str_c, sep = ", ") %>%
    mutate(participant_id = rating_raw$CASE) %>%
    pivot_longer(
      -participant_id,
      names_to = "question_id", values_to = "response"
    ) %>%
    bind_cols(keywords_for_rating, .) %>%
    pivot_longer(
      c(match, nonmatch),
      names_to = "condition", values_to = "keywords"
    ) %>%
    mutate(
      across(c(keywords, response), str_to_lower),
      keywords = str_replace_all(
        keywords, c(
          aufstemmen = "aufbrechen",
          tierkäfig = "käfig",
          wegkehren = "kehren",
          verühren = "rühren",
          schraubenschlüssel = "werkzeug",
          verquirlen = "rühren",
          tackern = "tacker",
          sprengstoffexplosion = "explosion",
          tankfüllstand = "füllstand",
          tonpott = "tongefäß",
          eierkarton = "eier verpackung",
          musikgerät = "musikinstrument",
          türgelenk = "scharnier",
          telegrafieren = "telegraf",
          sternenbilder = "sternbild",
          aufspulen = "aufwickeln",
          häckseln = "zerkleinern",
          `mikroskop-proben` = "mikroskop proben",
          streckenmaß = "maß",
          windgeschwindigkeit = "windstärke",
          nussöl = "nuss öl",
          entkörnen = "entkernen",
          katzenklo = "katze klo",
          kutschrad = "kutsche rad"
        )
      ),
      response = str_replace_all(
        response, c(
          aufhebeln = "aufbrechen",
          föhnen = "föhn",
          kasette = "kassette",
          aufkehren = "kehren",
          tackern = "tacker",
          sprayapparat = "spray apparat",
          anästhesieren = "betäuben",
          reaktionsspiel = "reaktion spiel",
          mulchgerät = "mulch gerät",
          makierung = "markierung",
          wissenschaftlich = "wissenschaft",
          spannwerkzeug = "werkzeug",
          wärmestab = "wärme stab",
          ampfel = "ampel",
          scheere = "schere",
          pflägen = "pflügen",
          knetten = "kneten",
          pfandkuchen = "pfannkuchen",
          anmacher = "anmachen",
          injezieren = "injizieren",
          telfon = "telefon",
          beschrifter = "beschriften",
          aufbewaren = "aufbewahren",
          spähne = "späne",
          separator = "trennen",
          stämpfer = "stampfen",
          fliente = "flinte",
          tromphete = "trompete",
          makieren = "markieren",
          stöbseln = "stöpsel",
          hiernwellen = "gehirnwellen",
          kartofeln = "kartoffeln",
          vaccum = "vakuum",
          saubermachen = "putzen",
          ankeln = "anker",
          schuessel = "schüssel",
          `zangen\\\\` = "zange",
          kleiderbuegel = "kleiderbügel",
          buerste = "bürste",
          buersten = "bürsten",
          druecken = "drücken",
          obstscheider = "obst schneiden",
          àumachen = "ausmachen",
          bieroeffner = "flaschenöffner",
          oeffnen = "öffnen",
          giesskanne = "gießkanne",
          gluehbirne = "glühbirne",
          schettem = "manschetten",
          kurzhantel = "kurzhanteln",
          tierekiste = "tiere kiste",
          kaffekocher = "kaffeemaschine",
          kinderwaagen = "kinderwagen",
          klobürste = "toilette bürste",
          orangenpresser = "orangen presse",
          foodmixer = "essen mixer",
          schuessel = "schüssel",
          naehen = "nähen",
          teigwalze = "nudelholz",
          pffefern = "pfeffer",
          maehen = "mähen",
          gesichtsbürste = "gesicht bürste",
          regenchirm = "regenschirm",
          kaesegratin = "käse gratin",
          slotsmaschine = "slot maschine",
          piggybank = "sparschwein",
          stampen = "kleben",
          arztwekzeug = "arzt werkzeug",
          gradskala = "grad skala",
          trichten = "trichter",
          spulsmaschine = "spülmaschine",
          zahnbrueste = "zahnbürste",
          bruesten = "bürsten",
          foltermaschine = "folter maschine",
          bieröffner = "flaschenöffner",
          oeffnen = "öffnen",
          pizzacutter = "pizza schneider",
          kerzestande = "kerzenständer",
          naehen = "nähen",
          geruest = "gerüst",
          nagelschneider = "nagel schere",
          burste = "bürste",
          bursten = "bürsten",
          loefel = "löffel",
          hamsterspielzeug = "hamster spielzeug",
          breadboard = "schneide brett",
          druceken = "drücken",
          nussknacnker = "nussknacker",
          ueberwachen = "überwachen",
          trainingsmaschine = "training maschine",
          padeln = "paddeln",
          schäumer = "aufschäumen",
          aufhanger = "aufhänger",
          hangt = "hängen",
          `eier-guillotine` = "eier messer",
          ruhrgerat = "rührgerät",
          katzentrager = "katzen träger",
          hinzufugen = "hinzufügen",
          kuchenform = "backform",
          nagelfeile = "nagel feile",
          fondues = "fondue",
          zuhoren = "zuhören",
          rasenmaher = "rasenmäher",
          geschlitzter = "schlitz",
          breifmarke = "briefmarke",
          bimmeln = "läuten",
          rasma = "",
          kassete = "kassette",
          nudelmaschine = "nudel maschine",
          ruhrer = "rührer",
          feuerloscher = "feuerlöscher",
          entfernungsmesser = "entfernung messer",
          heißluftpistole = "heißluft pistole",
          schuhlöffel = "schuhe anziehen",
          uben = "üben",
          naturlich = "natürlich",
          schißen = "schießen",
          rührgerät = "mixer",
          aufkehren = "kehren",
          rausziehen = "herausziehen",
          `mini-meißel` = "mini meißel",
          kaffeemischer = "kaffee mischer",
          nachttischlampe = "nachttisch lampe",
          arbeitsschlüssel = "arbeit schlüssel",
          `boom-box` = "lautsprecher",
          feststampfen = "fest stampfen",
          `casino-maschine` = "casino maschine",
          `herzfrequenz-test` = "herzfrequenz test",
          zaichnen = "zeichnen",
          schneidin = "schneiden",
          vergleichsmaschine = "vergleich maschine",
          rosenabzeichen = "rosen abzeichen",
          `dummy-stecker` = "dummy stecker",
          `post-punk-sanduhr` = "post punk sanduhr",
          schneidemaschine = "schneiden maschine",
          fusszeile = "fußzeile",
          gartenlampe = "garten lampe",
          trenneimer = "trennen eimer",
          fußabstreifer = "fußmatte",
          wichten = "gewicht",
          perlenständer = "perlen ständer",
          briefmarker = "briefmarke",
          `elektronische-schaltung` = "elektronische schaltung",
          fläschchenheizung = "flächen heizung",
          elektrodrucker = "elektro drucker",
          metalllinse = "metall linse",
          kugelheizung = "kugel heizung",
          abschrauber = "abschrauben",
          `mini-korb` = "mini korb",
          elektronenrechner = "elektronen rechner",
          spießfaum = "spieß",
          tierträger = "tier träger",
          rührgerät = "rührgerät",
          kuchenform = "backform",
          friteuse = "fritteuse",
          `ein-` = "ein",
          greigfen = "greifen",
          zerknittern = "falten bekommen",
          salatzange = "salat zange",
          wwrm = "wurm",
          duschwasser = "dusche wasser",
          verbreitene = "verbreiten",
          aufpieksen = "anstechen",
          restriktieren = "einschränken",
          rückgeld = "wechselgeld",
          aufkehren = "zusammenkehren",
          bratgut = "grillgut",
          bepinseln = "bestreichen",
          verquirlen = "vermischen",
          temparatur = "temperatur",
          aufspulen = "aufwickeln",
          elekronik = "elektronik",
          festnieten = "fest nieten",
          festspannen = "fest spannen",
          hebelkräfte = "hebelkraft",
          meiseln = "meißeln",
          betäüben = "betäuben",
          verschraüben = "verschrauben",
          schraüben = "schrauben",
          seperator = "trennen",
          schraübendreher = "schraubendreher",
          gegewicht = "gewicht"
        )
      ),
      cosine = compute_cosine(keywords, response, word2vec)
    )

@@

# # Test if all keywords and responses are in the embedding
# for (keywords in c(unique(rating$keywords), unique(rating$response))) {
#   if (!is.na(keywords)) {
#     for (word in (str_split(keywords, pattern = " |, ")[[1]])) {
#       if (!(word %in% rownames(word2vec))) {
#         cat(paste0(word, ' = "",\n'))
#       }
#     }
#   }
# }
